\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 using.tex
appease dave more

\begin{itemize}
        \item Use \texttt{tell\_landslide\_decide()} to indicate decision points.\footnote{
	We recommend at the start of \texttt{mutex\_lock} and at the end of \texttt{mutex\_unlock}, though it is also important to use one's own intuition, depending on which system call(s) are being tested.}
        \item Use \texttt{sched\_func} and \texttt{ignore\_sym} to make Landslide ignore global memory accesses, to enable better pruning.
        \item Use \texttt{DECISION\_INFO\_ONLY} to examine the set of decision points, and figure out which ones are irrelevant.
        \item Use \texttt{within\_func} and \texttt{without\_func} to make Landslide only use relevant decision points.
\end{itemize}

@@

\begin{itemize}
	\small
	\item \texttt{sched\_func}: When functions that make up the kernel's scheduler are identified, Landslide knows to ignore shared memory accesses from them. Accesses to scheduler data structures happen during {\em every} transition, so ignoring these is necessary for achieving any reduction at all.
	\item \texttt{ignore\_sym}: The user may wish to ignore memory accesses from other global data structures as well. For example, ignoring a mutex which is locked very frequently, but irrelevant to the actual test case, will result in an independence relation that \revision{enables much better state space reduction without losing the ability to find bugs in the parts of the kernel the user is interested in testing}.
	\item \texttt{within\_function}: If the user configures decision points to happen in common code paths, such as \texttt{mutex\_lock}, it will likely generate more branching than needed. For example, if testing \texttt{vanish}, there's no need to branch on a \texttt{mutex\_lock} in \texttt{exec}.

>>>>

\revision{
\begin{itemize}
        \item {\bf Indicating decision points.} Insert calls to \texttt{tell\_landslide\_decide()} in the guest kernel where Landslide should identify decision points.
        We recommend at the start of \texttt{mutex\_lock} and at the end of \texttt{mutex\_unlock}, though it is also important to use one's own intuition, depending on which system call(s) are being tested.
        \item {\bf Ignore always-conflicting memory locations.} Use \texttt{sched\_func} and \texttt{ignore\_sym} to identify shared memory locations that Landslide should ignore, to enable better pruning.
        \item {\bf Examine decision points.} Set \texttt{DECISION\_INFO\_ONLY} to make Landslide print the decision points instead of exploring. Examine the decision set, and figure out which ones are irrelevant to the test.
        \item {\bf Focus decision points.} Use \texttt{within\_func} and \texttt{without\_func} to specify which components of the kernel Landslide should identify decision points in, to reduce the state space and focus only on relevant interleavings.
\end{itemize}
}

@@

\begin{itemize}
	\small
	\item \texttt{sched\_func}: When functions that make up the kernel's scheduler are identified, Landslide knows to ignore shared memory accesses from them. Accesses to scheduler data structures happen during {\em every} transition, so ignoring these is necessary for achieving any reduction at all.
	\item \texttt{ignore\_sym}: The user may wish to ignore memory accesses from other global data structures as well. For example, ignoring a mutex which is locked very frequently, but irrelevant to the actual test case, will result in an independence relation that \revision{enables much better state space reduction without losing the ability to find bugs in the parts of the kernel the user is interested in testing}.
\end{itemize}

\revision{These configuration options enable the user to whitelist or blacklist certain components of the kernel for the purposes of identifying decision points.}

\begin{itemize}
	\item \texttt{within\_function}: If the user configures decision points to happen in common code paths, such as \texttt{mutex\_lock}, it will likely generate more branching than needed. For example, if testing \texttt{vanish}, there's no need to branch on a \texttt{mutex\_lock} in \texttt{exec}.
